jin_sim

### 2022-11-30 jin_sim.Rmd
Added day of flex code.

n <- length(china$days)   # number of observed days
m <- 150    # number of random outcomes
mu <- 1
sig <- 0.01  # the assumed measurement uncertainty is 10%
gau_sample <- matrix(rnorm(n*m, mu, sig), nrow=m, ncol=n)   # matrix of gaussian distribution

@@

## Day of flex (found with the fitted model)

```{r}
# trial 1
try <- mc_data[1,]
model_try <- nls(try ~ gauss_fn(days,a,b,c,d), data=china, start=list(a=10000,b=10000,c=0.1,d=1))
est_try <- summary(model_try)$parameters
est_try <- est_try[, 1]
names(est_try) <- NULL
fn_try <- function(x, ests) {ests[1]  + ests[2] * erf(ests[3] * x - ests[4])}

# find the second derivative of fitted function
# source: https://proofwiki.org/wiki/Derivative_of_Error_Function
erf_deriv <- function(x) {2/sqrt(pi)*exp(-x^2)}
fn_try_deriv <- bquote(.(est_try[2]) * 2/sqrt(pi) * exp(-(.(est_try[3]) * x - .(est_try[4]))^2))
fn_try_deriv <- D(fn_try_deriv,'x')
x=1:67
tmp <- eval(fn_try_deriv)
min(which(tmp < 0))
```

```{r}
# trial 1
try <- mc_data[1,]
model_try <- nls(try ~ gauss_fn(days,a,b,c,d), data=china, start=list(a=10000,b=10000,c=0.1,d=1))
est_try <- summary(model_try)$parameters
est_try <- est_try[, 1]
names(est_try) <- NULL
fn_try <- function(x, ests) {ests[1]  + ests[2] * erf(ests[3] * x - ests[4])}

# find the second derivative of fitted function
# source: https://proofwiki.org/wiki/Derivative_of_Error_Function
erf_deriv <- function(x) {2/sqrt(pi)*exp(-x^2)}
fn_try_deriv <- bquote(.(est_try[2]) * 2/sqrt(pi) * exp(-(.(est_try[3]) * x - .(est_try[4]))^2))
fn_try_deriv <- D(fn_try_deriv,'x')
x=1:67
tmp <- eval(fn_try_deriv)
min(which(tmp < 0))
```

@@

```{r}
temp_data <- mc_data[3,]
  # for each day
for (j in 1:(n-1)){
    num_diff[j] <- temp_data[j+1] - temp_data[j]
}

for (j in 1:(n-1)){
  if (num_diff[j+1] < num_diff[j]){
    print(j)
    break
  }
}
```

>>>>

n <- length(china$days)   # number of observed days
m <- 150    # number of random outcomes
mu <- 1
sig <- 0.1  # the assumed measurement uncertainty is 10%
gau_sample <- matrix(rnorm(n*m, mu, sig), nrow=m, ncol=n)   # matrix of gaussian distribution

@@

## Day of flex (trial)

```{r}
# trial 1
try <- mc_data[5,]
model_try <- nls(try ~ gauss_fn(days,a,b,c,d), data=china, start=list(a=2200,b=2200,c=0.1,d=1))
est_try <- summary(model_try)$parameters
est_try <- est_try[, 1]
names(est_try) <- NULL
fn_try <- function(x, ests) {ests[1]  + ests[2] * erf(ests[3] * x - ests[4])}

# find the second derivative of fitted function
# source: https://proofwiki.org/wiki/Derivative_of_Error_Function
erf_deriv <- function(x) {2/sqrt(pi)*exp(-x^2)}
fn_try_deriv <- bquote(.(est_try[2]) * 2/sqrt(pi) * exp(-(.(est_try[3]) * x - .(est_try[4]))^2))
fn_try_deriv <- D(fn_try_deriv,'x')
x=seq(1,67,length.out=6700)
tmp <- eval(fn_try_deriv)
min(x[tmp < 0])
```

## Day of flex (complete)

```{r}
flex_day <- rep(NA, m)
for (i in 1:m){
  try <- mc_data[i,]
  model_try <- nls(try ~ gauss_fn(days,a,b,c,d), data=china, start=list(a=2200,b=2200,c=0.1,d=1))
  est_try <- summary(model_try)$parameters
  est_try <- est_try[, 1]
  names(est_try) <- NULL
  fn_try <- function(x, ests) {ests[1]  + ests[2] * erf(ests[3] * x - ests[4])}

# find the second derivative of fitted function
# source: https://proofwiki.org/wiki/Derivative_of_Error_Function
  erf_deriv <- function(x) {2/sqrt(pi)*exp(-x^2)}
  fn_try_deriv <- bquote(.(est_try[2]) * 2/sqrt(pi) * exp(-(.(est_try[3]) * x - .(est_try[4]))^2))
  fn_try_deriv <- D(fn_try_deriv,'x')
  x=seq(1,67,length.out=6700)
  tmp <- eval(fn_try_deriv)
  flex_day[i] <- min(x[tmp < 0])
}
flex_day
```

@@
